\begin{frame}
  \frametitle{Effects}

  The PCE training program targets \structure{improving your thinking capacity} and your \structure{memory},
  it supports your \structure{intuition},
  increases your \structure{performance} and has a positive effect on your \structure{communication capacity}.
  Last but not least, these exercises strengthen your \structure{regeneration capacity} and your \structure{self healing
    capacity}.

  A \structure{regular training} of the exercises in the given order will lead to a \structure{rejuvenating effect}
\end{frame}
%--------------------------------------------------------------------------------------------------------------

\begin{frame}
  \frametitle{The Rune Exercises}

  The first six exercises are called the \structure{rune exercises}.
  They are modeled after the \structure{rune rites} of the Germanic tribes of old.
  Already the Edda talked about rune wisdom, which can be achieved either by the spoken words or certain finger or body postures.


  For simplicity's sake we name the rune exercises by their Latin letters.

  \end{frame}
%--------------------------------------------------------------------------------------------------------------

\begin{frame}
  \frametitle{Effects of the Rune Exercises}

  
  They bring the natural \structure{life energy}, the energy which as always present in our bodies, into an unobstructed \structure{flow}.
  They also help to \structure{deconstruct muscular tension} and \structure{activate the function of you glands}.
  They also help you to achieve \structure{harmony and equilibrium}.
  The life energy which is constantly flowing gets channeled and activated.
  These exercises are also suited for elderly people, they can't trigger any unwanted side effects.
  

\end{frame}
%--------------------------------------------------------------------------------------------------------------

%--------------------------------------------------------------------------------------------------------------

\begin{frame}
  \frametitle{Experimental Confirmation}

  The effectiveness of the exercises could be confirmed by bovis analysis,
  psychogenic brain field and
  electromyography (EMG) measurements on the corresponding body parts.

  In contrast to the other tested practice programs, the results were surprising.
  Beginners, practicing one day other energy rites and the next day the rune exercises scored significantly better.
\end{frame}

%--------------------------------------------------------------------------------------------------------------

\begin{frame}
  \frametitle{The Power Exercise}
  
  The 7th exercise, the power exercise activates your inner "power plant", your "life energy generator". We develop further into it, in the frame work of our examination about sexuality and the orgasm. 
  
  By tensing the PC muscle in the right way, an increased amount of life energy streams through the spine, the nerves and the tissue through every cell of the body.
  The rune exercises render the physical structures of our body conductive to the life energy and these structures allow the life energy to circulate through our body in a uninhibited way.
  
  This leads to a measurable charging of the brain with all it's positive effects. This power exercise is the only exercise known to me, which heightens the energetic level of a human in a quick and sustainable way.
\end{frame}

%--------------------------------------------------------------------------------------------------------------

\begin{frame}
\frametitle{Orientation in Space}

Before you start these exercises, use a compass and find the cardinal direction west. Mark in which direction west is, as you want to be oriented in this  direction during this training.
By the means of bio--electrical measurements and potential measurements on acupuncture points it has been confirmed that west is energetically the best position to practice these exercises. The measurements show that in comparison to other orientations, the inner activity is increased by about 30\%.
\end{frame}
