\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}

\item What is stress?
\item  Is stress acting only negatively?
\item How does the body react to stress?
\item Name a few examples of coping strategies.
\item Explain the 3 phase model of stress.
\item Which role has the limbic system in the regulation of stress?
  \vspace{0.4cm}
\item Why can't we think anymore under the influence of stress?
\item  Our senses get their signals over certain stimuli. Talk about it.
\item Strain can lead to stress. Discern different cases.
\item Upon stress, we react with defense reactions. Which ones?
  \vspace{0.4cm}
\item Classify the stressors and name a few examples of each category.
\item Ongoing Strain can lead to physical affects. Which ones?
  \vspace{0.4cm}
\item What does the term salutogenesis mean? Which signification does it hold for you?
  \vspace{0.4cm}
\item Encounter stress with movement. Justify!
  \vspace{0.4cm}
\item What does is mean to be mindful/attentive?
\item In which points does mindfulness differ from other forms of meditation?
\item Distinguish the two main forms of meditation.
\item Instruct a sitting meditation. Just focus on the start.
\item Which conditions do we need to look at in a sitting meditation?
\item Your thoughts are wandering during a meditation. Do you have a recipe to stay present?
\item There's many possibilities in the body--scan. How can you approach these possibilities?
  \item What are those possibilities?
  \item What is a body--scan?
  \item Which obvious advantages do you gain by getting up early in the morning?
    What are the disadvantages and eventual conditions? How do you proceed?
  \item Are you able to consciously wake up in the morning? What does ``consciously wake up in the morning'' mean for you?
    \vspace{4mm}
  \item Which are your five most important levels of stress regulation? Order them in a way that makes sense for you.
  \item Can you name ten of the twenty tips from Porta's text?
    \vspace{4mm}
  \item Name the positions of the sun salute.
  \item Which kind of people would you recommend practicing the sun salute?
    \vspace{4mm}
    \item Stress is also an economical factor and consideration. Explain!


\end{document}
