\input{Headers/ExercisesH} % ExercisesH, ExerciseswNotesH, ExercisesHandoutH, NotesH
% (= SlidesH, SlideswNotesH, HandoutH, NotesH, Slides2ScreensH,
\graphicspath{{images/}} % Location of the slide background and figure files

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title{Exercises} % The short title appears at the bottom of every slide, the full title is only on the title page

\input{../author}
\begin{document}

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}
%Learning

\begin{frame}
\frametitle{Learning}
\begin{itemize}
\item[-] \href{run:./PACE_presentation.pdf}{\underline{PACE}}
(\href{run:./PACE_Handout_student.pdf}{\underline{Student}} and 
\href{run:./PACE_Handout_instructor.pdf}{\underline{Instructor Handout}})
 (\textit{crossover, integrating both hemispheres, meridians, proprioception})\\
 learning capacity and readiness, hand--eye coordination, waking up,  reconnects emotions and neocortex, calm.
 
\item[-] \href{run:./Metacognitive_Instructor.pdf}{\underline{Metacognitive Exercises}} 
(\href{run:./Metacognitive_Student.pdf}{\underline{Student Handout}} and
\href{run:./Metacognitive_Exercises.pdf}{\underline{Practice Sheets}})
 (\textit{train mental capacities})\\
Train intellect, perception, thinking capacity and psyche, improve thinking speed, awake state and stress dominant traits.
 \end{itemize}
\end{frame}
%------------------------------------------------------
\begin{frame}
\frametitle{Physical Exercises}
\begin{itemize}
%General 
\item[-] \href{run:./Morning_Program.pdf}{\underline{Small morning program}} \\
Gets you ready in the morning. Wakes up, gets you in shape.
\item[-] \href{run:./Gravity_Glider.pdf}{\underline{Gravity glider}} 
 (\textit{stretch, relaxation})\\
Blood and lymph circulation, posture, equilibrium, coordination, \\
Comprehension.
% New slide: Energy exercises
% Energy flow harmonisation
\item[-] Sun salutation (not as handout)
 (\textit{stretch, rooting, energy})\\
Harmonizes the energy, makes the energy flow, stretches the meridians (energy connections in your body) \\
Rooting, activating the energy system.
\item[-] \href{run:./Rune_Exercises.pdf}{\underline{Rune Exercises}} 
 (\textit{stretch, rooting, energy})\\
Harmonizes the energy, gets you ready for a new start or idea \\
Rooting.
% PCE training, I have the PCE in the day
% Meridian Exercises
% Shi Shin Jitsu?
% Central pillar/stream
% Big hug
% Rest of the tibetans.
 \end{itemize}
\end{frame}
%------------------------------------------------------
\begin{frame}
\frametitle{Posture}
\begin{itemize}
\item[-] \href{run:./Posture.pdf}{\underline{Posture}}
(\href{run:./Posture_Handout.pdf}{\underline{Handout}}
and 
(\href{run:./Posture_wNotes.pdf}{\underline{Instructor version}})  
\item[-] 
\href{run:./Active_Stance.pdf}{\underline{Active Stance}}
(\href{run:./Active_Stance_Handout.pdf}{\underline{Handout}}) 
(\textit{Posture, abductor training, stretch})
Stretches the shortened muscles and trains the abductors.


\end{itemize}
\end{frame}
%------------------------------------------------------
\begin{frame}
\frametitle{Equilibrium and Statolith exercises}
\begin{itemize}
%Statolith
\item[-] \href{run:./Equilibrium_Exercises.pdf}{\underline{Equilibrium exercises}} 
with theory
(\href{run:./Equilibrium_Exercises_Handout.pdf}{\underline{Student handout}})
 (\textit{equilibrium, activate statolith ball, proprioception, posture})\\
Train statolith and equilibrium, induce relaxation.


\item[-] \href{run:./Headstand.pdf}{\underline{Headstand and preeliminary exercises}} 
 (\textit{activate statolith ball, equilibrium, posture})\\
Train statolith and equilibrium, induce relaxation.

\item[-] \href{run:./Statolith_rotation.pdf}{\underline{Statolith rotation}} 
 (\textit{activate statolith ball, equilibrium, proprioception})\\
Train statolith and equilibrium.
\end{itemize}
\end{frame}
%------------------------------------------------------
\begin{frame}
\frametitle{Mindfulness and Meditation}
\begin{itemize}

\item[-] \href{run:./Mindfulness_Meditation.pdf}{\underline{Mindfulness and Meditation}} 
(\href{run:./Mindfulness_Meditation_Handout.pdf}{\underline{Handout}})
 (\textit{meditation theory, mindfulness})\\
% Presentation with big blue half of screen, no drawings

%Meditation
\item[-] \href{run:./Sun_Breathing.pdf}{\underline{Sun Breathing}} 
 (\textit{breathing, meditation, mood, inner smile})\\
Removing negative emotions, filling up with good energy.
\item[-] \href{run:./Sitting_Meditation.pdf}{\underline{Sitting Meditation}} 
 (\textit{breathing, meditation, mood})\\
The basic meditation.
% With nice hand drawn pictures, ok
\item[-] \href{run:./Bodyscan.pdf}{\underline{Body Scan}} \href{run:./Bodyscan_guided.pdf} ({\underline{Guided Body Scan, PDF}}) 
 (\textit{bodily sensations, focus length and precision, meditation,})\\
Scanning the body, developing the focus of attention.

\item[-] \href{run:./HeartCoherence.pdf}{\underline{Heart Coherence Exercises}} \href{run:./HearthCoherence_guided.pdf} ({\underline{Guided Heart Coherence Exercise, PDF}}) 
 (\textit{Bring heart and brain into coherence})\\
Equilibrium between sympathetic and parasympathetic NS, quick exercise to get back into coherence.

% \item evtl Autogenic Training
\end{itemize}
\end{frame}

%------------------------------------------------------
\begin{frame}
\frametitle{Remove Tension}
\begin{itemize}

\item[-] \href{run:./Mindfulness_Meditation.pdf}{\underline{Breathing Exercises}} % Have to still adapt that,...
(\href{run:./Mindfulness_Meditation_Handout.pdf}{\underline{Handout}})
 (\textit{meditation theory, mindfulness})\\
% Presentation with big blue half of screen, no drawings

\end{itemize}
\end{frame}


\end{document} 
