\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}

\index{exercise!breathing exercises}\label{Ex:BreathingEx}
Already the breath only can optimize situations of tension which occurred.
Do you belong to the very relaxed and balanced people who could profit from more tension\index{effect!tension!regulate}
or more to the active up to overactive, which can't let go of their tension.
Choose your exercise!

\begin{enumerate}
\item \emph{Build up tension,} for instance in the case or tiredness:

  Close the left nostril and inhale through your right one.
  To exhale you close the right nostril and exhale through the left one.

\item \emph{Lower tension:}

  Close the right nostril and inhale through the left one.
  To exhale you close the left nostril and exhale through the right one.

\item \emph{Balance tension:}

  Close the left nostril and inhale through your right one.
  To exhale you close the right nostril and exhale through the left one.

  Then you change:
   Close the right nostril and inhale through the left one.
  To exhale you close the left nostril and exhale through the right one.

\end{enumerate}

Most often, the best ways to regulate stress are exercises, but they are only efficient when practiced on a regular base.\index{practice!regular base}
Hopefully such an instruction provides enough insight for concerned people in order to keep the exercises up.
Most people are better able to stay on track, when you speak of a \emph{ritual},\index{ritual} that they incorporate into their day.
Where is the difference? --- In the Way of looking at it!

Give yourself now (detailed!) instructions for your own ritual!


\end{document}