\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}



Signals which are sent by the heart to the brain also influence the limbic system and the cerebral cortex and vice versa.
According to scientists views, it is possible for the heart to make a connection of emotions and intellect and to help in an intelligent handling of the emotions.\index{effect!emotios, intelligent handling}
Research shows that already a memory of a pleasant feeling or even just an imagined scene is enough to induce the transition between a chaotic heart rate to reach
coherence\footnote{coherent: connected}\index{heart!coherence}.

The results of labor tests studying heart rate rhythms in connection in with different emotions of the test subjects show a correlation between
incoherent\footnote{incoherent: not connected} heart rate frequency patterns and negative emotions like stress, fear, frustration, worries and anger.
Positive feelings on the other side show a coherent and well ordered heart pattern.

That corresponds to a serene, relaxed but alert state,\index{effect!state, serene but alert}
which has positive influence on the immune system\index{effect!immune system!psotivie influence} and the hormonal equilibrium of the body\index{effect!hormon, equilibrate}.
This is the goal, to reach this ideal state of mind.
When the \emph{heart and the emotional brain agree}, the autonomous nervous system stabilizes\index{effect!autonomous nervous system},
which leads in turn to an equilibrium between the sympathetic and the parasympathetic nerve.

Such an interaction leads to a feed--back, which helps that with a bit of practice the maximal heart coherence can be maintained up to thirty minutes.
With intense practice, building up coherence get progressively easier; with times you will almost be able to communicate directly with your heart.\index{effect!communication, with your heart}

As an effect we are able to effectively support our health\index{effect!health, support}, support healing processes\index{effect!healing processes, support}
and increase our intake capacity for learning\index{effect!learning!capacity increase} with heart coherence exercises and meditation techniques.

These exercises are about bringing yourself into a state of
gratitude, love, sympathy and recognition.\index{effect!gratitude}\index{effect!love}\index{effect!sympathy}\index{effect!recognition}
In this manner we are able to percieve the voice of the heart and to find cooperative solutions for our problems.\index{effect!solution, cooperative}
Heart and brain is coing into unison and we get access to our often unused and not recognized ressources.

\epigraph{Most folks are as happy as they make up their minds to be.}{\textit{Abraham Lincoln}}


\end{document}