\documentclass[12pt]{article}
\setlength\parindent{0pt}
%\usepackage{gensymb} % for the \degree sign in front of C
%\usepackage{amsmath} % Ttypeset Math
%\usepackage[makeroom]{cancel} % To have the ability to use \cancel and \bcancel to cross out units
%Gummi|065|=)
\title{The Bodyscan}
\author{Kilian Schmid, translated Raphael Nussbaum}

\date{}
\begin{document}

\maketitle
\noindent (10 -- 15 min)

\vspace{4mm}
In this exercise I don't have to perform, nothing has to be done. It's just about perceiving myself as a whole. I will explore all the perceptions and the feelings of my body with an alert, interested and foremost accepting attitude.

\vspace{6mm}
That can help me to relax physically and mentally, to live more consciously and to center my thoughts and perception in the here and now.

\vspace{6mm}
I can put myself in a comfortable position, close the eyes and put the hands down along my body with the palms up and open. I put my legs as comfortable as possible and breathe calmly through the nose. I'm allowed to only exist, nothing has too be achieved, just being here.

\vspace{6mm}
I take myself the time to focus for a while only that I'm here and now, in this moment.

\vspace{6mm}
In this moment, the only thing which exists is me in the silence. Me, completely resting in myself, full of calm strength, serene and peaceful.

\vspace{6mm}
I let go of all other thoughts, all other feelings.\\
All painful memories\\
All sorrows and fears\\
All grudges and jealousies\\
Everything which bothers me about myself\\
Instead a feeling of peace, security and harmony flows through me.

\vspace{6mm}
With every inhale the feeling of calm strength reinforces, with every exhale the feeling of peace, security and harmony gets reinforced.

\vspace{6mm}
My breath is flowing calmly and relaxed into me and the same calm way out of me. I attentively perceive the abdominal wall, how it widens on the inhale and sinks back on the exhale.

While exhaling, the contact to the floor intensifies. I let myself flow into the ground while exhaling.

\vspace{6mm}
My attention is on my left foot, the ankle joint, the lower leg, the knee, the thigh.

\vspace{6mm}
I perceive my whole leg, deep into the hip joint.

\vspace{6mm}
I perceive my right hip joint.

\vspace{6mm}
I perceive my right foot, my right ankle, the lower leg and the thigh. 

I feel deep into my hip joint.

\vspace{6mm}
How are my buttocks lying on the support? How does the floor feel?

\vspace{6mm}
How does my pelvic floor feel like, the whole pelvis, the tail bone and the sacrum?

\vspace{6mm}
I become aware of the lower back with the lumbar region. Without any expectations I breathe into it and out of it, and accept it as it is, all the tensions, all the perceptions. I breathe into it and out of it.

\vspace{6mm}
My focus widens to the whole back, the width of the back, the shoulders and the chest.

\vspace{6mm}
I feel my whole back, from the shoulders to the hip.

\vspace{6mm}
Attentively I observe the movement in my belly, the activity of the colon, the stomach area.

\vspace{6mm}
How are my rips feeling and my sternum, the whole chest area, the movement of breath? I perceive the space of the lungs and the hearth. I observe all the feelings of my hearth. 

\vspace{6mm}
I widen my focus to the shoulders, the arms, the hands, the finger, forearm, the upper arm, the arm pits and the shoulders. I'm completely present.

\vspace{6mm}
I feel my neck, I perceive the space between my throat and my neck, the spine. I feel the way the back of my head is resting on the floor. I feel my ears, my face, my lips, the nose, the cheeks, the eyes, the way they rest in my eye sockets, my forehead.

\vspace{6mm}
My entire face is full of peace.

\vspace{6mm}
I feel my scalp with the bone of the skull, the hair.

\vspace{6mm}
I feel the highest point of my head, the crown. Totally relaxed, I imagine the breath flowing in through this point, let it flow through my body and then flow out of my feet. Then I let it flow in through my feet and out of my crown.I attentively observe the breath flowing through my body. I'm totally present, I perceive my body as a whole, myself as a whole. No worries, no fears, no negative feelings can separate me as a whole. 

\vspace{6mm}
A feeling of deep joy and happiness spreads in me.

\vspace{6mm}
Now I'm focussing my attention again on my body, the space and am again in the here and now.

The calm and the deep happiness I keep and am happy to be just am I am.

\vspace{6mm}
I count from the number 7 to 1 and am totally present here.

I slightly move my fingers, my hands, slowly open my eyes, roll my head and stretch languorously. 

\end{document}
