%------------------------------------------------------------


\begin{frame}
\frametitle{Song of Myself.  Walt Whitman: Leaves of Grass}
``\textit{I exist as I am, that is enough, \\
If no other in the world be aware I sit content,\\
And if each and all be aware I sit content.\\
One world is aware, and by the far the largest to me, and that is myself,\\
And whether I come to my own today or in ten thousand or ten million years,\\
I can cheerfully take it now, or with equal cheerfulness, I can wait.}''
\end{frame}
%------------------------------------------------------------
%------------------------------------------------------------

title{Acceptance}


\frametitle{Negative Feelings} 
\begin{itemize}

\frametitle{Why would I do that?}

\frametitle%------------------------------------------------------------
\section{Practice}

\begin{frame}
\frametitle{How can you practice Mindfulness?}
There's {two ways} to practice Mindfulness and both are important to integrate it in our live.
\begin{itemize}
\item In the {formal practice} specific methods get applied. It helps us to stay present in the moment for a longer period of time.
\item Then there's the {informal practice}. There it's all about remembering to be present during daily activities and to check once in a while, if you're really present. 
\end{itemize}
Mindfulness is more a {mode of being} than a technique. Basically it's the question, if and to what degree do you want to {be present at the unfolding of your own life}.  
\end{frame}

%------------------------------------------------------------
\subsection{Formal Practice}
\begin{frame}
\frametitle{Formal Practice}
There's many different types of formal meditation. 
\begin{itemize}
\item The so--called {Body--Scan} (Perception of the whole body, reclined)
\item {Sitting Meditation}, 
\item and different position of Hatha-Yoga, (they are executed in a slow, gentle and mindful manner). For instance the sun salutation. 
\end{itemize}
They are just different doors, which all lead into the same room.

%I will focus here on the Sitting Meditation, because it can be practised everywhere. 
\end{frame}

%------------------------------------------------------------

\begin{frame}
\frametitle{Common Traits}
\begin{itemize}
\item The {mindfulness of breathing} is common to these three methods.
\item Every formal Meditation practise has a {focus point} onto which the attention gets directed.
\item Normally it doesn't take long for the the {mind to wander off}, no matter how motivated we were to not let it happen. Every single time this happens, we {take notice} (as unjudgemental as possible) to where the mind has wandered, before we direct the mind {back to the object of focus}.
\item We might notice that we were busy with a memory, a future fantasy or a bodily perception or that we were affected of feelings of boredom, impatience or fear.
\end{itemize}
\end{frame}

%------------------------------------------------------------
\subsection{Informal Practice}
\begin{frame}
\frametitle{Informal Practice}
The time and effort dedicated to formal practice helps to {stay present} in very the moment in daily life. 

\begin{itemize}
\item  In theory, it is very easy, but it is hard to make it into a {daily routine}. We have the habit to pass a good amount of our lives mindlessly on {autopilot}, entangled with our own thoughts, and feelings, our moods and reaction to things. Only seldom we're able to see the bigger picture.
\item We are dealing with {habits} here. It is hard to break habits. The best way to go about it is to practice and {empower a new, alternate habit}.
\end{itemize}
\begin{block}{Quote Marc Aurel}
``\textit{ Inside of you! Inside of you is a source of goodness which never stops to bubble, as long and you don't stop digging.}''
\end{block}
\end{frame}
%------------------------------------------------------------

\begin{frame}
\frametitle{Life is your teacher}
Mindfulness is just a {moment--to--moment awareness}, therefore every ``mundane'' task can be an opportunity to practise:
\begin{itemize}
\item  Eating
\item Brushing your teeth
\item Cleaning the dishes,
\item Walking
\item Driving
\item Tax declaration and cleaning up after your dog in the park...
\end{itemize}
The wonderful advantage is that we don't need to put additional time aside.
\end{frame}
%------------------------------------------------------------

\begin{frame}
\frametitle{Change in Consciousness}

\textbf{All what's needed is a change in consciousness. A flick of the switch from a habit--driven blind  mode of being to {awake presence}.}

In this mode, daily {life becomes practice, our meditation master and coach}.


\vspace{3.5cm}
Back to \href{run:./Exercises.pdf}{\underline{exercises}}.

\end{frame}

%------------------------------------------------------------


