\documentclass[../Book.Stress_regulation.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}
\section{5 Different Forms of Stress Regulation}
\index{stress regulation}
\begin{enumerate} 
\item  Daily {training of your body}\index{training} and your body awareness, to become {strong and robust}.
\item {Breathe\index{breathe} deeply} and calmly: Make every morning a gift to your body and soul, a unit of calmness and awareness, so that they beat in unison with your hearth.\\
When {thoughts} are tormenting you, observe them and write them down, or let them flow freely like a creek.
\item {Be aware}\index{awareness!body} of your body and its signals. How well do you feel getting up, at work, while eating, on the way home, in the evening by yourself?\\
Your body speaks the {language of your soul}. Be aware of what you add to your body and your soul.
\item Give the {gift of your smile}\index{smile} and laughter to the world. If you're not feeling like it, be brave and do in anyway.\\
Be aware of how the world changes.
\item Be aware of your {words}\index{awareness!words} and use them consciously: be mindful of how you speak with yourself, about how you think about and judge yourself and others.\\
Influence yourself with {positive thinking}\index{thinking!positive}. 
\end{enumerate}




\mytextbox[0]{Here Prof. Dr Sepp Porta\index{Porta, Sepp}~\cite{PortaStress} describes how to get the stress a bit under control.

Simple, but makes a lot of sense:

  \vspace{5mm}

\subfile{Porta_Stress-Hormones_text}}
\epigraph{I prefer meeting a happy person than finding a five pound bill. A cheerful human being spreads good mood around himself and when she/he enters a room, it's as if a light got lit.}{\textit{Robert Louis Stevenson}, translation from German}

\end{document}