\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}

Imagine, you won in a contest the following price:
\begin{center}
  Every morning the bank puts \$86,400 into an account at your disposition.
\end{center}

Like every game, this game has rules, too:

\begin{enumerate}
\item The money you didn't spend gets taken away again at the end of the day. You can't wire that money to another account, you only can spend it. Every morning, you get a new account with \$86,400
\item The bank can terminate that game at any moment without notice. The game is over. They close the account and you won't get a new one.
\end{enumerate}

\subsection{What Would You Do?}

You'd buy everything you ever wanted? Not just for you but for people close to you or even people you don't know given that this is too much to spend all by yourself, isn't it?
You'd try to spend every cent, to use it in a way?

Generally, this game is reality. Everybody of us has such a magical ``bank account'', we're just not aware of it. This magical bank is time. Every morning we wake up we get a gift of 86,400 seconds of life for the day. Leftover time doesn't carry over or can be saved. What we didn't live of it this day is lost forever.
Every morning the account fills up again, but the bank can terminate the game at any time without prior notice.

What are you going to do with your 86,400 seconds? Aren't they much more valuable than the same amount of money?

\begin{center}
  \textbf{So, start living your life!}
  \end{center}

\end{document}