\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}


If you imagine a landscape in blue, it has a different effect on you, than if you imagine a landscape in red. Colors\index{color} carry a statement, even if they don't get felt by all people in the same way and intensity. So, colors can \emph{transmit} a quality, but they can \emph{support} us with their quality.

A possible categorization for the colors:

\begin{description}
\item[Red:] The color of the vital will to action, of love,  emotionality, assertiveness, excitation and passion.
\item[Orange:] The color of self--confidence and of creativity, of warmth and ambition, of power and zest for action.
\item[Yellow:] The color of thinking, sensitivity, of the mind, being full of ideas and ideals, changes, the wish of liberation, hope and expecting happiness.
\item[Green:] The color of introspection, of freedom. It contains peacefulness, adaptability, being in equilibrium, serenity, sensitivity, open--mindedness and happy detachment.
\item[Blue:] Shows, calmth, peace, the need to recover, openness, silence, fidelity, depth, selflessness and capacity to surrender.
\item[Indigo:] Indigo is the color of the belief, the capacity to immerse, security, of the silent existence. Social thinking and actions are associated with this color. it contains also humanity, altruism, charity, sincerity, honesty, and justice. 
  \item[Violet:] Religious feelings, serve, self--sacrifice, abstinence and asceticism lie in this highest color. Mystics, insight, perfection and salvation are attributed to this color.
  \end{description}

  This choice of colors wasn't done in an arbitrary way, they are the colors of the rainbow.
  Many people are persuaded, the part of the human body are the subtle energy center (``chakras''),\index{chakras} which are often represented as rotating vortexes.
  Each of these energy center has a color associated and a gland of the human body, depending on it's location.

 \begin{table}[htb]
  \centering
  \begin{tabular}{llll}
    Root--chakra & between genitals and anus & adrenals & red \\
    Sacral--chakra & below the navel & gonads & orange \\
    Solar plexus--chakra & above the navel & pancreas & yellow \\
    Heart--chakra & middle of the chest & thymus gland & green, pink \\
    Throat--chakra & on the throat & thyroid gland & light blue \\
    Third eye--chakra & between the eye brows & pituitary gland & indigo blue \\
    Crown--chakra & top part of the head & pineal gland & violet, white
  \end{tabular}
  \caption{The chakras of the human body.}
\end{table}


\epigraph{I don't mind almost believing that you can feel colors; their unique quality would only be confirmed even more. You can also taste them. Blue becomes alkaline, a yellow--red would taste sour. All manifestations of the essentiality are related.}{\textit{Johann Wolfgang von Goethe}}


\end{document}