\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}

\chapter{Introduction}

If you eat well--balance you create an important foundation for your health and well-being.
If it's bread, milk, meat, fruit or veggies --- it's the proportions and balance which matters.
If you eat healthy you feel it, you feel fresh and full of energy.\index{healthy food}

The bustle and stress of our modern way of life leads to us humans taking less and less time for the sourcing and preparation of food.
Important knowledge about production, composition, origin and seasonal availability gets lost.
We tend to eat more and more fast food, functional food and other industrially produced products.
We consume too much energy--dense food items with a high calorie content and at the same time we tend to move less.
The daily intake in calories exceeds the use by the body. This leads to over--weight which is the cause for many food related health problems.
Examples are diseases of the hearth and circulation, metabolism problems like hyper acidity and diabetes type 2 up to metabolic syndrome.
Over--weight is one of the biggest stressors of our time, as can be seen by the never ending stream of new diets.

This part will lead you from anatomy and physiology of nutrition to determine your ideal, healthy body weight and determine the ideal composition of your daily food.
You will get information about the most important nutrition--related disorders and how stress and nutrition is related.
Information of a few selected foods and selected nutrition tables help you putting your nutrition together\footnote{We will at times refer to DACH reference values. D--A--CH stands for the German speaking associations for nutrition and research on nutrition from Germany, Austria an Switzerland~\cite{DACH}.}.

\section{Learning Goals}

\begin{outline}
  \1 To know the main constituents of our food und
  \2 being able to name them
  \2 give examples of them
  \2 explain what they're used for in the human body
  \1 Dietary supplements
  \2 explain why dietary supplements are necessary
  \2 the meaning of:
  \3 understand omega 3 fatty acids and being able to explain is
  \3 understand dietary supplements in relation to stress
  \1 Understand and being able to explain the acid--base metabolism
  \2 it's relation to homeostasis
  \2 what is a latent acidosis
  \2 which means of stress regulation positively influence the acid--base metabolism
  \1 Being able to explain the relation between nutrition and stress
  \2 why does stress tends to lead to gaining weight
  \2 why do high GLYX foods lead to gain weight
  \1 Understand and being able to explain specific terms
  \2 essential
  \2 pH--value
\end{outline}


\section{Anatomy and Physiology of Nutrition}
(Translated passage from Anatomie--Atlas~\cite{AAtlas})
\subsection{Voyage Through the Body}
Olfactory cells detect the roast, they locate toast compounds, the marjoram and so on.
They stimulate the flow of the juices into the mouth, get you excited for the first bite.
In the hypothalamus\index{hypothalamus} in the brain is the seat of the central of the appetite, which directs all the processes.
It gets information from the body about how high the blood sugar levels are, from the fat cell if they need replenishment.
That is the seat of the somatic intelligence (body--centered intelligence)\index{somatic intelligence}.
The ancient knowledge of the body, which knows what the body needs.
Unfortunately, that part of us is asleep in most of us.
It should coordinate hunger, cravings and satiation; we move a lot, we need a lot of calories.
The hypothalamus directs a whole army of hunger--saturation hormones\footnote{Almost weekly science discovers a new one.}.\index{hormones!hunger--satiation}
Either it's 'eat more', or if we have a sedentary period it switches to the energy save program --- satiation sets in earlier.
This ancient wisdom urges us with craving of lemons, if the immune system needs a vitamin C boost or a craving for cheese if the bones needs calcium.
The problem is that we suppressed this ancient wisdom because we're not eating anymore due to being hungry but due to what time dictates.
It is suppressed because we're not eating anymore what he body needs but empty calories, jazzed up with artificial aromas.
The head says, 'I want apple pie'. But that's not what the body says, the apple pie isn't good for it. It'd prefer the apple by itself.
That's what in the genetic program, that what fits with the metabolism.

The hypothalamus in the brain, the central of appetite registers how much fat is in the fat cells and how much sugar in the blood. If it finds something missing, it provoques hunger.

\end{document}