\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}

With malnutrition over a longer time, we run the risk of getting sick, in any form, physical or psychologically.
The risk of a nutrition caused disease can be significantly reduced through a  healthy and adequate diet,
and by doing so we provide the requirements for the daily high usage to body and psyche.

\subsection{What is a Healthy Diet?}

The basis of a healthy nutrition is a supply of energy and nutrients in the sense of a full--fledged diet,
based on the needs and the load of the individual.
Under full-fledged we mean a quantitaviely and qualitatively balanced selection of diverse foods,
which are beneficial to our health and supplies our organism with all vital nutrients.
A full--fledged diet also considers technological, ecological and social aspects.
It differs from the rgular mixed diet by consciously choosing foods which:
\begin{itemize}
\item are regional
\item seasonally available
\item which do without additives
\item are produced ecologically and/or livestock--friendly (organic products)
\item which are processed, packed and transport in an environment friendly manner
  \item warrant a fair price/income (ie. coffee from Max Havelar)
  \end{itemize}

  That means in short: Food as close to it's natural state as possible, seasonal and from the region
  prepared in a gentle manner and in the amount, which correspond to the amounts given by the food pyramid (MyPlate).
  
\end{document}