\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}


If you eat well--balance you create an important foundation for your health and well-being.
If it's bread, milk, meat, fruit or veggies --- it's the proportions and balance which matters.
If you eat healthy you feel it, you feel fresh and full of energy.\index{healthy food}

The bustle and stress of our modern way of life leads to us humans taking less and less time for the sourcing and preparation of food.
Important knowledge about production, composition, origin and seasonal availability gets lost.
We tend to eat more and more fast food, functional food and other industrially produced products.
We consume too much energy--dense food items with a high calorie content and at the same time we tend to move less.
The daily intake in calories exceeds the use by the body. This leads to over--weight which is the cause for many food related health problems.
Examples are diseases of the hearth and circulation, metabolism problems like hyper acidity and diabetes type 2 up to metabolic syndrome.
Over--weight is one of the biggest stressors of our time, as can be seen by the never ending stream of new diets.

This part will lead you from anatomy and physiology of nutrition to determine your ideal, healthy body weight and determine the ideal composition of your daily food.
You will get information about the most important nutrition--related disorders and how stress and nutrition is related.
Information of a few selected foods and selected nutrition tables help you putting your nutrition together\footnote{We will at times refer to DACH reference values. D--A--CH stands for the German speaking associations for nutrition and research on nutrition from Germany, Austria an Switzerland~\cite{DACH}.}.


\section{Learning Goals}

\begin{outline}
  \1 To know the main constituents of our food und
  \2 being able to name them
  \2 give examples of them
  \2 explain what they're used for in the human body
  \1 Dietary supplements
  \2 explain why dietary supplements are necessary
  \2 the meaning of:
  \3 understand omega 3 fatty acids and being able to explain is
  \3 understand dietary supplements in relation to stress
  \1 Understand and being able to explain the acid--base metabolism
  \2 it's relation to homeostasis
  \2 what is a latent acidosis
  \2 which means of stress regulation positively influence the acid--base metabolism
  \1 Being able to explain the relation between nutrition and stress
  \2 why does stress tends to lead to gaining weight
  \2 why do high GLYX foods lead to gain weight
  \1 Understand and being able to explain specific terms
  \2 essential
  \2 pH--value
\end{outline}

\end{document}