\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}

I encourage the reader to work through the text and write up your own questions, which sum up this unit.
Here some questions as an inspiration.

\section{Questions to Nutrition}

\begin{enumerate}
\item What happens with food, when we ingest it?
\item Describe the stations of it's journey through our body.
\item What are the most important mistakes we make eating?
\item How do our eating habits differ from our ancestors? How is that related with these mistakes?
\item What are the components of the human body's energy needs?
\item How can I find my basic energy turnover?
\item What are PAL values, how do I calculate them and how do they affect my total metabolic rate?
\item What is a ``normal'' body weight and how can I calculate it?
\item What's the Brocca formula, the BMI, WHR and the normal weight?
\item What are the main constituent of the nutrition, what's their importance and the daily required amount?
  \begin{itemize}
  \item Water
  \item Fats
  \item Carbohydrates
  \item Vitamins

    Name the most important vitamins, in which foods they are contained, why they are important and the daily required dose.

  \item Minerals

    Name the most important minerals, in which foods they are contained, why they are important and the daily required dose.
    \item Fibers
  \end{itemize}
\item ``antioxidant'', ``protects the body from free radicals'' what does that mean?
\item When and why are nutritional supplements necessary/important?
\item Which supplements would you recommend in case of stress, fatigue or exhaustion?
\item Or for sleeping problems?
\item What do you understand under the term ``healthy nutrition''?
\item What's the food pyramid and what does it tell us?
\item Which point do you have to pay attention to to loose weight or maintain a healthy body weight?
\item What is the GLYX and what is it's effect on the human body?
\item What's the glycemic index and what do you have to pay attention to?
\item Tips for a healthy nutrition
  \item What is to be said about
    \begin{itemize}
    \item Coffee?
    \item Green tea?
    \item Fruit and vegetable juices?
    \item Milk?
      \item Meat?
      \item Salt?
        \item Sugar?
    \end{itemize}
    \item What is a latent acidosis and how does it develop?
    \item What are the symptoms, effects of, diagnosis and treatment of the latent acidosis?
    \item What is diabetes?
      \item What is the relation between stress and nutrition?
    \item How can you help your body regulate stress with your nutrition?
    \item What can be said about vegetarianism?
    \item And about Low-Carb?
    \item What is the nutrition according to 5 elements?
    \item The 5 tastes.
    \item Which foods act basic/alkaline in our body?
      \item Name a few tips for a healthy nutrition. How many can you come up with?
\end{enumerate}

\end{document}
