\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}

Having to constantly endure stress, fears and sorrows makes you gain weight.
Moments of shock, physical or emotional overtaxed and injuries of any kind automatically trigger our survival program\index{survival program}.
This innate survival program is as old as living being themselves, and it doesn't matter if an aggressive bear or an overdue tax declaration
is threatening us.
No matter if real hunger drives us out to forage and hunt nights after nights or if it's mobbing or the overdrawn bank account.
It can be a real enemy with real weapons threatening us and our family or the the fear of a test which freezes us up.
We can get hurt in a real combat of by words or gestures.
No matter if others despise and disapprove of you, or if it is you yourself who despises and disapproves of you.
Our organism always reacts with the same program: our survival mode.
Our  organism wants to either fight, act, hide or flee.

\section{What Happens in the Human Body?}

\subfile{StressFoodBody.tex}

\section{Tricks for Nutrition by while Stress}

\subfile{StressFoodTips.tex}

\section{Summary Stress and Nutrition}

\begin{itemize}
\item Food which is eaten in a hectic manner becomes a stressor
\item Keep an eye on the glycemic index and the glycemic load of foods
\item  Coffee and black tea increase the heart activity too much and increase nervousness
\item Meat contains arachidonic acid and increases the acidity of the body
\item The fear contained in meat (through the killing process, maybe how the cattle was kept) will
  spread to the human
\item Eat dark chocolate (above 70\% cocoa content) in acute stress moments
\item When feeling without energy, eat foods full of energy, fresh and whole foods
\end{itemize}

\end{document}
