\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}

\clearpage
\thispagestyle{empty}
% \SI[parse-numbers=false]{\text{\ensuremath{


\begin{sidewaystable}[p!]
  \caption{Table Vitamins, page 2}
  \centering
  \begin{small}
  \begin{tabularx}{\textwidth}{p{2cm}p{4.5cm}p{6cm}p{2.5cm}p{1cm}p{2cm}}
    \toprule
    \textbf{Name} & \textbf{Signification} & \textbf{Deficiency Syndrome} & \textbf{Contained in} & \textbf{Solubility} & \makecell[{p{1.5cm}}t]{\textbf{RDA} \\ \textbf{(EU-RDA):}} \\
    \midrule
    \makecell[{p{2cm}}t]{\textbf{Vitamin B6}\index{vitamin!B6} \\ (Pyridoxine)} &
    Important for the metabolism, brain and nerves. &
    Increased excitability, cramps, inflammations of the skin and nerves &
    Wheat bran, skins of natural rice, vegetables, potatoes, egg yolks, yeast, soy beans, whole wheat grains, meat, fish &
    Water soluble &
    \SI{2}{\mg} \\
%    \hline
    \makecell[{p{2cm}}t]{\textbf{Folic acid}\index{vitamin!folic acid} \\ (Vitamin B9 or B11)} &
    Important for growth, cell reproduction, especially of the red blood cells. Regulates the homocysteine balance. &
    Disturbances of the cell division, impairment of blood cell formation, sediments on the arterial walls through the disturbed homocysteine balance,
    impairments in hair growth, changes in mucous membranes. An insufficiency in folic acid is often caused by a disturbed resorption in the colon or
    taking of barbiturates or anti baby pills. &
    Whole wheat products, leafy greens, strawberries, cauliflower, red beets, soy, milk, eggs, innards. &
    Water soluble & \SI{0.2}{\mg} \\
    %        \hline
    \makecell[{p{2cm}}t]{\textbf{Vitamin B12}\index{vitamin!B12} \\ (Cobalamin)} &
    Important for the formation of the blood corpuscles. &
    Changes in the blood pictures of the red cells. &
    Milk, cheese, eggs, liver, meat &
    Water soluble & \SI{0.001}{\mg} \\
    \makecell[{p{2cm}}t]{\textbf{Vitamin C}\index{vitamin!C} \\ (Ascorbic acid)} &
    Important for the collagen synthesis, wound healing, healthy muscle systems, blood vessels, strengthening of the immune system, resorption of iron,
    neutralizes free radicals (antioxidants). &
    Scurvy, susceptibility for infections &
    Citrus fruits, rose hip, fresh vegetables, bell pepper and especially in sea buckthorn and the acerola cherry. & Water soluble & \SI{60}{\mg} \\
    \rowcolor{lightgray}\makecell[{p{2cm}}t]{\textbf{Vitamin D}\index{vitamin!D} \\ (Calciferol)\\ is build from pro--vitamin D stored in the skin through sun light} &
    Calcium intake isn't possible without vitamin D &
    Decalcification of the bones, rachitis & Butter, egg yolks, liver, cod liver oil, fish & Fat soluble &
    \makecell[{p{2cm}}t]{\SI{0.005}{\mg} \\ (\SI{1}{\mg} = 40,000 IU) \\ Overdosing leads to dangerous calcium deposits in the body} \\
    \bottomrule
  \end{tabularx}
  \end{small}
  \end{sidewaystable}
\clearpage
\thispagestyle{empty}
% \SI[parse-numbers=false]{\text{\ensuremath{


\end{document}
