\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}
\clearpage
\thispagestyle{empty}
% \SI[parse-numbers=false]{\text{\ensuremath{


\begin{sidewaystable}[p!]
  \caption{Table Vitamins}
  \centering
  \begin{tabularx}{\textwidth}{p{2.5cm}p{4.5cm}p{5.5cm}p{3cm}p{1.5cm}p{1.5cm}}
    \toprule
    \textbf{Name} & \textbf{Signification} & \textbf{Deficiency Syndrome} & \textbf{Contained in} & \textbf{Solubility} & \makecell[{p{1.5cm}}t]{\textbf{RDA} \\ \textbf{(EU-RDA):}} \\
    \midrule
    \rowcolor{lightgray}\makecell[{p{2.5cm}}t]{\textbf{Vitamin A}\index{vitamin!A} \\ (Retinol)\\  Pro--vitamin A (Carotene) will be metabolized into vitamin A in the organism} &
    Important for the eyes, generation of cells, protection of free radicals, body's defenses and procreation. &
    {Night blindness, eye damage} &
    {Butter, liver, and as pro--vitamin A in carrots, red bell pepper, tomatoes and spinach.} &
    Fat soluble &
    \makecell[{p{1.5cm}}t]{\SI{0,8}{\mg} \\
      (\SI{1}{\mg} = 3300 IU) \\
      Overdosing can be harmful!}\\
    \hline
    \makecell[{p{2.5cm}}t]{\textbf{Vitamin B1}\index{vitamin!B1} \\ (Thiamine, aneurin)} &
    Important for a healthy nervous system, properly working carbohydrate and fat metabolism.
    At high dosages (about \SI{1000}{\mg}) it has a protective effect against mosquitoes, through decomposition products in the sweat. &
    Stomach and colon disturbances, tiredness, difficulties in the functions of the nervous system, difficulties focusing, depressions, Beriberi = muscle weakness, inflammations of the nerves &
    Yeast, skins of whole wheat grains, potatoes, soy beans, legumes, meat &
    Water soluble &
    \SI{1.4}{\mg} \\
    \hline
    \makecell[{p{2.5cm}}t]{\textbf{Vitamin B2}\index{vitamin!B2} \\ (Riboflavin)} &    
    Important for the conservation of the tissue, eyes, skin and mucous membrane and for the formation of enzymes and the metabolism &
    Changes of the skin, inflammations of the edges of the mouth, brittle finger nails &
    Milk, whole wheat grains, eggs, meat, fish &
    Water soluble & \SI{1.6}{\mg} \\
    \hline
    \makecell[{p{2.5cm}}t]{\textbf{Vitamin B3}\index{vitamin!B3} \\ (Niacin, vitamin PP)} &
    Important for the operation of the digestive tract, the metabolism, the nerves and the skin. Dilates the blood vessels. &
    Problems and inflammations of the nervous system, the skin and the mucous membranes. Pellagra = skin changes (rough) with simultaneous disturbances of the stomach and colon.
    Often with a deficiency of other B vitamins &
    Peanuts, Whole wheat grains, ;legumes, yeast, salmon, chicken &
    Water soluble&
    \SI{18}{\mg} \\
        \hline
        \makecell[{p{2.5cm}}t]{\textbf{Vitamin B5}\index{vitamin!B5} \\ (Pantothenic acid)} &
        Important for the skin. External application in ointments to promote wound healing. Usage after operations, to reactivate the colon.&
        Bad healing of wounds, problems with the colon &
        Whole wheat products, legumes, peanuts, eggs, yeast, liver &
        water soluble &
        \SI{6}{\mg} \\
        \hline
  \end{tabularx}
  \end{sidewaystable}

\end{document}
