\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}
\clearpage
\thispagestyle{empty}
% \SI[parse-numbers=false]{\text{\ensuremath{


\begin{sidewaystable}[p!]
  \caption{Table Vitamins}
  \centering
  \begin{tabularx}{\textwidth}{p{2.5cm}p{4.5cm}p{5.5cm}p{3cm}p{1.5cm}p{1.5cm}}
    \toprule
    \textbf{Name} & \textbf{Signification} & \textbf{Deficiency Syndrome} & \textbf{Contained in} & \textbf{Solubility} & \makecell[{p{1.5cm}}t]{\textbf{RDA} \\ \textbf{(EU-RDA):}} \\
    \midrule
    \rowcolor{lightgray}\makecell[{p{2.5cm}}t]{\textbf{Vitamin A}\index{vitamin!A} \\ (Retinol)\\  Pro--vitamin A (Carotene) will be metabolized into vitamin A in the organism} &
    Important for the eyes, generation of cells, protection of free radicals, body's defenses and procreation. &
    {Night blindness, eye damage} &
    {Butter, liver, and as pro--vitamin A in carrots, red bell pepper, tomatoes and spinach.} &
    Fat soluble &
    \makecell[{p{1.5cm}}t]{\SI{0,8}{\mg} \\
      (\SI{1}{\mg} = 3300 IU) \\
      Overdosing can be harmful!}\\
%    \hline
    \makecell[{p{2.5cm}}t]{\textbf{Vitamin B1}\index{vitamin!B1} \\ (Thiamine, aneurin)} &
    Important for a healthy nervous system, properly working carbohydrate and fat metabolism.
    At high dosages (about \SI{1000}{\mg}) it has a protective effect against mosquitoes, through decomposition products in the sweat. &
    Stomach and colon disturbances, tiredness, difficulties in the functions of the nervous system, difficulties focusing, depressions, Beriberi = muscle weakness, inflammations of the nerves &
    Yeast, skins of whole wheat grains, potatoes, soy beans, legumes, meat &
    Water soluble &
    \SI{1.4}{\mg} \\
%    \hline
    \makecell[{p{2.5cm}}t]{\textbf{Vitamin B2}\index{vitamin!B2} \\ (Riboflavin)} &    
    Important for the conservation of the tissue, eyes, skin and mucous membrane and for the formation of enzymes and the metabolism &
    Changes of the skin, inflammations of the edges of the mouth, brittle finger nails &
    Milk, whole wheat grains, eggs, meat, fish &
    Water soluble & \SI{1.6}{\mg} \\
%    \hline
    \makecell[{p{2.5cm}}t]{\textbf{Vitamin B3}\index{vitamin!B3} \\ (Niacin, vitamin PP)} &
    Important for the operation of the digestive tract, the metabolism, the nerves and the skin. Dilates the blood vessels. &
    Problems and inflammations of the nervous system, the skin and the mucous membranes. Pellagra = skin changes (rough) with simultaneous disturbances of the stomach and colon.
    Often with a deficiency of other B vitamins &
    Peanuts, Whole wheat grains, ;legumes, yeast, salmon, chicken &
    Water soluble&
    \SI{18}{\mg} \\
%        \hline
        \makecell[{p{2.5cm}}t]{\textbf{Vitamin B5}\index{vitamin!B5} \\ (Pantothenic acid)} &
        Important for the skin. External application in ointments to promote wound healing. Usage after operations, to reactivate the colon.&
        Bad healing of wounds, problems with the colon &
        Whole wheat products, legumes, peanuts, eggs, yeast, liver &
        water soluble &
        \SI{6}{\mg} \\
\bottomrule
  \end{tabularx}
  \end{sidewaystable}

\clearpage
\thispagestyle{empty}
% \SI[parse-numbers=false]{\text{\ensuremath{


\begin{sidewaystable}[p!]
  \caption{Table Vitamins, page 2}
  \centering
  \begin{tabularx}{\textwidth}{p{3cm}p{4cm}p{5.5cm}p{2.5cm}p{1.5cm}p{2.7cm}}
    \toprule
    \textbf{Name} & \textbf{Signification} & \textbf{Deficiency Syndrome} & \textbf{Contained in} & \textbf{Solubility} & \makecell[{p{1.5cm}}t]{\textbf{RDA} \\ \textbf{(EU-RDA):}} \\
    \midrule
    \makecell[{p{3cm}}t]{\textbf{Vitamin B6}\index{vitamin!B6} \\ (Pyridoxine)} &
    Important for the metabolism, brain and nerves. &
    Increased excitability, cramps, inflammations of the skin and nerves &
    Wheat bran, skins of natural rice, vegetables, potatoes, egg yolks, yeast, soy beans, whole wheat grains, meat, fish &
    Water soluble &
    \SI{2}{\mg} \\
%    \hline
    \makecell[{p{3cm}}t]{\textbf{Folic acid}\index{vitamin!folic acid} \\ (Vitamin B9 or B11)} &
    Important for growth, cell reproduction, especially of the red blood cells. Regulates the homocysteine balance. &
    Disturbances of the cell division, impairment of blood cell formation, sediments on the arterial walls through the disturbed homocysteine balance,
    impairments in hair growth, changes in mucous membranes. An insufficiency in folic acid is often caused by a disturbed resorption in the colon or
    taking of barbiturates or anti baby pills. &
    Whole wheat products, leafy greens, strawberries, cauliflower, red beets, soy, milk, eggs, innards. &
    Water soluble & \SI{0.2}{\mg} \\
    %        \hline
    \makecell[{p{3cm}}t]{\textbf{Vitamin B12}\index{vitamin!B12} \\ (Cobalamin)} &
    Important for the formation of the blood corpuscles. &
    Changes in the blood pictures of the red cells. &
    Milk, cheese, eggs, liver, meat &
    Water soluble & \SI{0.001}{\mg} \\
    \makecell[{p{3cm}}t]{\textbf{Vitamin C}\index{vitamin!C} \\ (Ascorbic acid)} &
    Important for the collagen synthesis, wound healing, healthy muscle systems, blood vessels, strengthening of the immune system, resorption of iron,
    neutralizes free radicals (antioxidants). &
    Scurvy, susceptibility for infections &
    Citrus fruits, rose hip, fresh vegetables, bell pepper and especially in sea buckthorn and the acerola cherry. & Water soluble & \SI{60}{\mg} \\
    \rowcolor{lightgray}\makecell[{p{3cm}}t]{\textbf{Vitamin D}\index{vitamin!D} \\ (Calciferol)\\ is build from pro--vitamin D stored in the skin through sun light} &
    Calcium intake isn't possible without vitamin D &
    Decalcification of the bones, rachitis & Butter, egg yolks, liver, cod liver oil, fish & Fat soluble &
    \makecell[{p{2.7cm}}t]{\SI{0.005}{\mg} \\ (\SI{1}{\mg} = 40,000 IU) \\ Overdosing leads to dangerous calcium deposits in the body} \\
    \bottomrule
  \end{tabularx}
  \end{sidewaystable}
\clearpage
\thispagestyle{empty}
% \SI[parse-numbers=false]{\text{\ensuremath{


\begin{sidewaystable}[p!]
  \caption{Table Vitamins, page 3}
  \centering
  \begin{tabularx}{\textwidth}{p{3cm}p{4cm}p{5.5cm}p{2.5cm}p{1.5cm}p{2.7cm}}
    \toprule
    \textbf{Name} & \textbf{Signification} & \textbf{Deficiency Syndrome} & \textbf{Contained in} & \textbf{Solubility} & \makecell[{p{1.5cm}}t]{\textbf{RDA} \\ \textbf{(EU-RDA):}} \\
    \midrule
    \rowcolor{lightgray}\makecell[{p{3cm}}t]{\textbf{Vitamin E}\index{vitamin!E} \\ (Tocopherol)} &
    The functions of the gonadal glands, circulation, procreation, protection of the blood vessels,
    for an elastic skin, against early onset aging, protection from harmful environmental factors and free radicals.
    Acts as antioxidants for highly unsaturated fatty acids, hormones and vitamins. &
    Disturbances of the procreation functions &
    Grain sprouts, wheat germ oil & Fat soluble &
    \makecell[{p{2.7cm}}t]{\SI{10}{\mg} \\ (\SI{1}{\mg} dl-alpha-tocopherolacetate = 1 IU) \\
        Important for the metabolism, brain and nerves.} &
    Increased excitability, cramps, inflammations of the skin and nerves &
    Wheat bran, skins of natural rice, vegetables, potatoes, egg yolks, yeast, soy beans, whole wheat grains, meat, fish &
    Water soluble &
    \SI{2}{\mg} \\
%    \hline
    \makecell[{p{3cm}}t]{\textbf{Biotin}\index{vitamin!biotin} \\ (Vitamin H or B7)\\ The gut bacteria can synthesize biotin. Raw proteins deactivate biotin.} &
    Important for the transformation of energy from food into body energy, building up or skin, hair and finger nails. &
    Dry skin with dandruff &
    Milk, eggs, whole wheat, soy beans, lamb, liver &
    Water soluble &
    \SI{0.15}{\mg} \\
%    \rowcolor{lightgray}\makecell[{p{3cm}}t]{\textbf{Vitamin K}\index{vitamin!K} \\ (Phytomenadione)\\
%      The gut bacteria can synthesize vitamin K. A damaged gut flora (antibiotics!\index{antibiotics}) can lead to an insufficiency.} &
%    Influences the blood clotting. Can decrease the effects of medication, which decrease the blood coagulation. &
%    Tendencies to bleed &
%    Cabbage family, spinach, broccoli, oats. &
%    Fat soluble &
%    \makecell[{p{2.7cm}}t]{\SI{0.07}{\mg} \\ Overdosing can be harmful!}
 \\
    \bottomrule
  \end{tabularx}
  \end{sidewaystable}

\end{document}
