\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}
\clearpage
\thispagestyle{empty}
% \SI[parse-numbers=false]{\text{\ensuremath{


\begin{sidewaystable}[p!]
  \caption{Table Vitamins, page 3}
  \centering
  \begin{small}
  \begin{tabularx}{\textwidth}{p{3cm}p{6.5cm}p{3cm}p{2.5cm}p{1cm}p{2cm}}
    \toprule
    \textbf{Name} & \textbf{Signification} & \textbf{Deficiency Syndrome} & \textbf{Contained in} & \textbf{Solubility} & \makecell[{p{2.7cm}}t]{\textbf{RDA} \\ \textbf{(EU-RDA):}} \\
    \midrule
    \rowcolor{lightgray}\makecell[{p{3cm}}t]{\textbf{Vitamin E}\index{vitamin!E} \\ (Tocopherol)} &
    The functions of the gonadal glands, circulation, procreation, protection of the blood vessels,
    for an elastic skin, against early onset aging, protection from harmful environmental factors and free radicals.
    Acts as antioxidants for highly unsaturated fatty acids, hormones and vitamins. &
    Disturbances of the procreation functions &
    Grain sprouts, wheat germ oil & Fat soluble &
    \makecell[{p{2cm}}t]{\SI{10}{\mg} \\ (\SI{1}{\mg} dl-alpha-to\-co\-phe\-rol\-ace\-tate = 1 IU)} \\
%    \hline
   \makecell[{p{3cm}}t]{\textbf{Biotin}\index{vitamin!biotin} \\ (Vitamin H or B7)\\ The gut bacteria can synthesize biotin. Raw proteins deactivate biotin.} &
   Important for the transformation of energy from food into body energy, building up or skin, hair and finger nails. &
    Dry skin with dandruff &
    Milk, eggs, whole wheat, soy beans, lamb, liver &
    Water soluble &
    \SI{0.15}{\mg} \\
    \rowcolor{lightgray}\makecell[{p{3cm}}t]{\textbf{Vitamin K}\index{vitamin!K} \\ (Phytomenadione)\\
      The gut bacteria can synthesize vitamin K. A damaged gut flora (antibiotics!\index{antibiotics}) can lead to an insufficiency.} &
    Influences the blood clotting. Can decrease the effects of medication, which decrease the blood coagulation. &
    Tendencies to bleed &
    Cabbage family, spinach, broccoli, oats. &
    Fat soluble &
    \makecell[{p{2cm}}t]{\SI{0.07}{\mg} \\ Overdosing can be harmful!}
 \\
    \bottomrule
  \end{tabularx}
  \end{small}
  \end{sidewaystable}

\end{document}
