\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}
% \SI[parse-numbers=false]{\text{\ensuremath{
% \SIrange[parse-numbers=false]{\text{\ensuremath{8\sfrac{1}{2}}}}{\text{\ensuremath{10\sfrac{1}{2}}}}{\cup}

\begin{longtable}{rp{10.5cm}l}
   & \textbf{Tip} & \textbf{Domain} \\
  \toprule
  \endhead
  1 & I start the day with a glass of (room temperature) water & Digestion \\
  2 & I drink \SIrange[parse-numbers=false]{2}{\text{\ensuremath{2\sfrac{1}{2}}}}{\liter}
  (\SIrange[parse-numbers=false]{\text{\ensuremath{8\sfrac{1}{2}}}}{\text{\ensuremath{10\sfrac{1}{2}}}}{\cup})
  water through the day, in small gulps & Nutrition \\
  3 & Alcohol is a luxury food item (but also addictive). Take care to consume it only in a conscious manner and in the context
  of a meal. & Dietary Behavior \\
  4 & I eat 5 portions of fruit and vegetables a day (3 port. vegetables and 2 port. fruits) & Nutrition \\
  5 & I consider the fat content of the foods & Nutrition \\
  6 & I buy seasonal available vegetables & Environment \\
  7 & I buy seasonal available fruit & Environment \\
  8 & I take care of having varied meals & Nutrition \\
  9 & I prefer whole wheat products & Nutrition \\
  10 & I buy organic products & Quality \\
  11 & I take care to prepare my food in a mild manner & Quality \\
  12 & I buy meat from the region & Environment \\
  13 & I buy fish from the region & Environment \\
  14 & I eat fish at least once a week & Nutrition \\
  15 & I avoid soft drinks & Nutrition \\
  16 & I take my time to eat & Dietary behavior \\
  17 & Well chewed is already half digested and helps to reduce stress! & Dietary behavior \\
  18 & I include fruits and vegetables of many different colors on my diet & Nutrition \\
  19 & With every meal, I eat a portion of whole wheat products, legumes, other grain based products or potatoes & Nutrition \\
  20 & I avoid sweets & Dietary behavior \\
  21 & I avoid salty snacks (ie. peanuts) & Dietary behavior \\
  22 & I don't work when I eat --- I don't eat when I work! & Dietary behavior \\
  23 & I buy as much as possible fresh vegetables and avoid cans or ready--to--eat products & Quality \\
  24 & I enjoy caffeinated drinks in moderation & Dietary behavior \\
  25 & Cold--pressed oils (extra vergine) & Quality \\
  26 & I eat a portion of nuts a day
  (=\SIrange{20}{30}{\gram},
  \SIrange[parse-numbers=false]{\text{\ensuremath{\sfrac{3}{4}}}}{\text{\ensuremath{1}}}{\oz})
  & Nutrition \\
  27 & I prefer plant based proteins over animal based fats & Quality \\
  28 & I make sure I have enough potassium in my diet & Nutrition \\
  29 & Fresh herbs as spices instead of spice mixes & Quality \\
  30 & I make sure to keep a ratio of 80\% to 20\% of base to acid producing foods in my diet & Nutrition \\
  31 & I prefer foods with a low glycemic index GI, and also consider the glycemic load GL & Nutrition \\
  32 & I take care to get daily movement, for instance a walk in the evening of at least half an hour & Movement \\
  33 & I consciously use stairs instead of the elevator. Instead of waiting the bus I can as well walk a stop & Movement \\
  34 & I look into the topic salt & Quality \\
  35 & I look into Omega--3 fatty acids & Quality \\
  36 & Do I get enough vitamins? & Quality \\
  37 & I also can eat healthy in a restaurant & Nutrition \\
  38 & The right posture, also while eating & Dietary behavior \\
  39 & One hot meal a day & Dietary behavior \\
  40 & I don't eat our of frustration & Dietary behavior \\
  41 & Three meals a day are enough & Dietary behavior \\
  42 & At least once a day, I should have e feeling of hunger before I eat. I don't just eat because it is time to do so. &
  Dietary behavior \\
  43 & I avoid artificially sweetened and light products & Nutrition \\
  44 & I only eat chocolate with a cocoa content of more than 70\%. & Quality \\
  45 & Only wash salads, don't soak them into water & Quality \\
  46 & I prefer steaming vegetables than boiling them in water & Quality \\
  47 & I make sure to keep the gluten intake low, and I prefer other gluten than from wheat & Nutrition \\
  48 & I include prebiotics, fibers and probiotics in my diet (fermented, live products) & Digestion \\
  49 & I enjoy my food, take the time for it and am grateful for it & Dietary behavior \\
  50\\
  51\\
  52\\
  53\\
  54\\
  55\\
\end{longtable}

\end{document}
