\documentclass[../main.tex]{subfiles}
\graphicspath{{\subfix{../images/}}}
\begin{document}


Maybe you got the impression after all these information, that we try you to become vegetarian.
That's not the intention of this book, unless you want to become a vegetarian.

It is definitely possible to have a diet healthy diet with small quantities of meat --- in the same way that a vegetarian diet is not necessarily healthy.
Somebody who eats no meat but only industrial food is definitely having a worse diet than a person with a diet of some meat and whole foods.

Albert Einstein said:
``It is my view that the vegetarian manner of living, by its purely physical effect on the human temperament, would most beneficially influence the lot of mankind.''

On thing to consider is that eating meat always requires killing of animals.
This can keep people who eat meat away from true happiness.
This is not perceivable, because we don't know the happier place as comparison.
But at one point or other does everybody know that killing is never part of being in the middle, the center and that it
removes us from true experience of love.

A little tip: If somebody wants to slowly transition to a vegetarian diet, is tofu a good choice.
Tofu is a good meat substitute with valuable plant based proteins, has very little fats and calories.
It's easily digestible and totally free of cholesterol.
Tofu is also ecologically sustainable.

\textbf{The root of the word vegetarian, vegetus means nothing else but ``full of life''.}

\subsection{Quotes of Famous Vegetarians}

Through history, there always have been voices which showed the importance of a vegetarian diet.


\vspace{5mm}
\noindent \textbf{Pythagoras} (570--495 BC, Greek mathematician and philosopher)
  ``For as long as men massacre animals, they will kill each other. Indeed, he who sows the seed of murder and pain cannot reap joy and love.''

\vspace{5mm}
\noindent \textbf{Horace} (65-8 BC, classical poet of Rome)

\noindent ``Dare to be wise! Stop killing animals!
He who postpones living rightly is like the rustic who waits for the river to run out before he crosses.''*

\vspace{5mm}
\noindent \textbf{Leonardo da Vinci} (1452--1519, Italian universal genius)

\noindent ``Truly man is the king of beasts, for his brutality exceeds them.
We live by the death of others. We are burial places.''
``I have from an early age abjured the use of meat, and the time will come when men such as I will look upon the murder of animals as they now look upon the murder of men.''

\vspace{5mm}
\noindent \textbf{Jean Paul} (1763--1825, German poet)

\noindent ``Because the heart beats under a covering of hair, fur, feathers, or wings, it is, for that reason, to be of no account?''
``Dear God! How many hours of martyrdom of animals does a human need to splice together one single minute of joy for his tongue.''*

\vspace{5mm}
\noindent \textbf{Wilhelm Busch} (1832-1908, German poet and painter, humorist)

\noindent ``There only will be true human culture, when not only eating of human beings but of any animal counts as cannibalism.''*

\vspace{5mm}
\noindent \textbf{Franz Kafka} (1883--1924, Austrian--Tschech writer)

\noindent ``Now I can look at you in peace; I don't eat you anymore.''
(While watching fish in an aquarium)

\vspace{5mm}
\noindent \textbf{Sven Hedin} (1865--1952, Swedish Asia--Researcher)

\noindent ``I never could get myself to snuff out a light of life, as I see myself incapable of lighting a new one.''*

\vspace{5mm}
\noindent \textbf{Albert Schweitzer} (1875--1965, theologian from the Alsace and missionary doctor, peace Nobel Price 1952)

\noindent ``We must fight against the spirit of unconscious cruelty with which we treat the animals. Animals suffer as much as we do. True humanity does not allow us to impose such suffering on them. It is our duty to make the whole world recognize it. Until we extend our circle of compassion to all living things, humanity will not find peace.''
``When man learns to respect even the smallest being of creation \ldots nobody has to teach him to love his fellow man. Compassion for animals is intimately connected with goodness of character, and it may be confidently asserted that he who is cruel to animals cannot be a good man.''

\vspace{5mm}
\noindent \textbf{Mahatma Gandhi} (1869--1948, Indian politician and proponent of nonviolent resistance)

\noindent ``I do feel that spiritual progress does demand at some stage that we should cease to kill our fellow creatures for the satisfaction of our bodily wants.''

\vspace{5mm}
\noindent \textbf{Isaac Bashevis Singer} (*1904, American writer, Nobel prize for literature 1978)

\noindent ``I did not become vegetarian for my health, I did it for the health of the chickens.'' ``To be a vegetarian is to disagree --- to disagree with the course of things today \ldots starvation, cruelty --- we must make a statement against those things. Vegetarianism is my statement. And I think it's a strong one.''

\vspace{5mm}
\noindent \textbf{Leo Tolstoi} (1828--1910, Russian writer)

\vspace{5mm}
\noindent ``Vegetarianism serves as the criterion by which we know that the pursuit of moral perfection on the part of humanity is genuine and sincere.'' and
``As long as there are slaughterhouses there will be battlefields.''

\footnotesize{* This quote has been translated from German}

\end{document}
